---
title: "Untitled"
author: "Volunteer"
date: "September 18, 2015"
output: html_document
---

```{r}
library(dygraphs)
library(ggplot2)
library(utils)
evita <- read.csv('Evita.csv', header = TRUE, sep =',')
evita$BeginDate = as.Date(evita$BeginDate, '%m/%d/%Y')
evita$EndDate = as.Date(evita$EndDate, '%m/%d/%Y')
drops = c("EntityID", "EnrollmentID")
evita = evita[,!(names(evita) %in% drops)]
```

# Plots

## Histogram of Gender

```{r, echo=FALSE}
  #dygraph(data = evita, aes(evita$Gender))
```

## Histogram of Race

```{r, echo=FALSE}
  ggplot(data = evita, aes(evita$Race)) + geom_histogram(breaks=seq(0,2,by=1))
```

## Histogram of Ethnicity

```{r, echo=FALSE}
  ggplot(data = evita, aes(evita$Ethnicity)) + geom_histogram(breaks = seq(0, 2, by = 1)) + xlab('Gender') + ylab('Count') + labs(title='Histogram of Ethnicity')
```


## Histograms Age and Entry/Exit
```{r, echo=FALSE}
ggplot(data=evita, aes(evita$AgeEntry)) + geom_histogram(breaks = seq(18, max(evita$AgeEntry), by = 3)) + geom_freqpoly(col='red')
ggplot(data=evita, aes(evita$AgeExit)) + geom_histogram(breaks = seq(18, max(evita$AgeExit), by = 3)) + geom_freqpoly(col='red')
```

## Histograms of Length of Stay and ln of Length of Stay
Length of Stay takes on an exponential distribution, a ln transformation of the data gives it a more normal distribution

```{r, echo=FALSE}
ggplot(data=evita, aes(evita$LOS)) + geom_histogram()
evita$LogLOS = log(evita$LOS)
ggplot(data=evita, aes(evita$LogLOS)) + geom_histogram() + geom_freqpoly(col='red')
```

## $\Chi^{2}$

```{r, echo=FALSE}
  tmpEvita <- subset(evita, Race != -99 & Gender != -99 & Ethnicity != -99)
  head(tmpEvita)
  tbl <- as.table(rbind(c(tmpEvita$Race, tmpEvita$Gender, tmpEvita$Ethnicity, tmpEvita$LOS)))
  Xsq <- chisq.test(tbl)
  Xsq
  tbl <- as.table(rbind(c(tmpEvita$Race, tmpEvita$Gender, tmpEvita$LOS)))
  Xsq <- chisq.test(tbl)
  Xsq
  tbl <- as.table(rbind(c(tmpEvita$LOS)))
  Xsq <- chisq.test(tbl)
  Xsq
```

****

## Kolmogorov-Smirnov Tests

The Kolmogorov Smirnov Tests determine if two continuous distributions are equal.

```{r}
  work = subset(evita, JobTraining == 1)
  nowork = subset(evita, JobTraining == 0)
  KS = ks.test(nowork$LOS, work$LOS, "exponential", alternative = 'g')
  KS
  plot(ecdf(nowork$LOS), col="red")
  plot(ecdf(work$LOS), add=TRUE, lty="dashed", col="green")
```

With a p-value of `r eval(KS$p.value)` it is determined that CDFs of the Length of Stay for those who under go job training and those who do not are not the same.